### 2019-08-22 maciek.tex
Omega(kl)

\section{Lower bound $\Omega(\ell)$}

@@

In this section we assume the Online Balanced Partition problem with the existence of a perfect partition of the input graph.

\begin{theorem}
  The competitive ratio of any deterministic algorithm for Online Balanced Partition (with perfect partition) is $\Omega(k\cdot \ell)$.
\end{theorem}

>>>>

In this section we consider the Online Balanced Partition problem.
We show a lower bound of $\Omega(k \cdot \ell)$ that uses an input that has a perfect partition.
Therefore, this result is a lower bound for the general Online Balanced Partition problem, as well as a lower bound for Online Balanced Partition with perfect partition.
The latter complements an upper bound $O(k \cdot \ell)$ for Online Balanced Partition with perfect partition that we present in Section TODO.

\begin{theorem}
  The competitive ratio of any deterministic algorithm for Online Balanced Partition is $\Omega(k\cdot \ell)$.
\end{theorem}

\maciek{ToDo}

\section{Trash: old versions etc.}

\subsection{Lower bound $\Omega(\ell)$}

\maciek{The most recent version of the lower bound is in $\Omega(l\cdot k)$ section. This is an early version!}

@@
